A data-intensive assessment of the species-abundance distribution.

### 2015-04-02 defense_pres.tex

\subsubsection{Data Collection}
\subsection{Compiled Data}
\begin{frame}[t]{}
\frametitle{Data}
Inclusion criteria:
\begin{itemize}
\item Quantitative abundances
\item Animals
\item Complete sampling
\item Must not be heavily summarized or processed
\item High degree of taxonomic resolution
\item Observational
\end{itemize}
\end{frame}

@@

\subsection{Data Availability}
\begin{frame}[t]
\frametitle{Data}
~\\
~\\
The final community abundance database is publicly available and importable through the EcoData Retriever.\\ 
(http://www.ecodataretriever.org/)
\end{frame}

@@

\subsection{Forms of the distribution}
\begin{frame}
\frametitle{Forms of the SAD}
\begin{large}
Model classes:
\end{large}
\begin{itemize}
\item Purely statistical
\item Branching process
\item Population dynamics
\item Niche partitioning
\item Maximum entropy
\item Feasible set/combinatorics
\end{itemize}
\end{frame}

>>>>

\subsubsection{Data Collection}
\begin{frame}[t]{}
\frametitle{Data}
Inclusion criteria:
\begin{itemize}
\item Quantitative abundances
\item Animals
\item Complete sampling
\item Must not be heavily summarized or processed
\item High degree of taxonomic resolution
\item Observational
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{Data wrangling}
\begin{center}
\includegraphics[scale=.27]{./sad-data/dissertation/Wrangling.png}
\end{center}
\begin{tiny}
Cavitt 2000.
\end{tiny}
\end{frame}

@@

\subsection{Data Availability}
\begin{frame}[fragile]
\frametitle{Data Availability}
~\\
~\\
Public \& open access through figshare.\\
EcoData Retriever importable.\\
\begin{verbatim}
(http://figshare.com)
(http://www.ecodataretriever.org)
\end{verbatim}
\includegraphics[scale=.3]{./sad-data/dissertation/retriever_logo_wtext.png}
\includegraphics[scale=.5]{./sad-data/dissertation/figshare_FullColour.jpg}
\end{frame}

@@

\subsection{Forms of the distribution}
\begin{frame}
\frametitle{Forms of the SAD}
Statistical description\\  
\includegraphics[scale=.2]{./sad-data/dissertation/Preston1948.png}\\

\begin{tiny}
Preston 1962a.\\
\end{tiny}

Process-based\\
\includegraphics[scale=.25]{./sad-data/dissertation/Rosindelletal2011.png}\\

\begin{tiny}
Rosindell et al. 2011.
\end{tiny}
\note{
\begin{itemize}
\item Purely statistical (Lognormal, logseries)
\item Branching process (Zipf)
\item Population dynamics (Neutral theory)
\item Niche partitioning (Geometric)
\item Maximum entropy
\item Feasible set/combinatorics
\end{itemize}}
\end{frame}
